### 2018-01-04 UOW_thesis_template_v2-0/thesis_template/chapters/euroComp.tex
:wrench: Removing the blue text after Marianito's approval

\section{Generalised example: straddle-on-a-call compound option}
We outlined in Section~\ref{sec:gen} that the results in Corollary 1 can be implemented for any financial payoff in options pricing to generate any compound option pricing formula. This is attainable since any of the aforementioned payoffs can be expressed as finite linear combinations of the functions
	\begin{equation}
		\label{eqn:funcs}
		x \mapsto \1_I(x), \quad x \mapsto x\1_I(x),
	\end{equation}
where $\1_I$ is the indicator function defined as
	\begin{equation*}
		\1_I(x) = \begin{cases}
			1, \quad x \in I, \\
			0, \quad x \notin I,
		\end{cases}
	\end{equation*}
and where $I$ is an arbitrary interval with endpoints $a$ and $b$ with $a < b$. The interval can be open, half-closed, or closed. \textcolor{blue}{The two auxiliary functions in~\eqref{eqn:funcs} are the building blocks for many financial payoffs in options pricing.} For example, a call option has a payoff $\max(x-K,0)$ which can be written as
	\begin{equation*}
		\max(x-K,0) = x\1_{[K,\infty)}(x) - K\1_{[K,\infty)}(x),
	\end{equation*}
where the interval $I$ is $[K,\infty)$.

>>>>

\section{Generalised example: straddle-on-a-call compound option}
We outlined in Section~\ref{sec:gen} that the results in Corollary 1 can be implemented for any financial payoff in options pricing to generate any compound option pricing formula. This is attainable since any of the aforementioned payoffs can be expressed as finite linear combinations of the functions
	\begin{equation}
		\label{eqn:funcs}
		x \mapsto \1_I(x), \quad x \mapsto x\1_I(x),
	\end{equation}
where $\1_I$ is the indicator function defined as
	\begin{equation*}
		\1_I(x) = \begin{cases}
			1, \quad x \in I, \\
			0, \quad x \notin I,
		\end{cases}
	\end{equation*}
and where $I$ is an arbitrary interval with endpoints $a$ and $b$ with $a < b$. The interval can be open, half-closed, or closed. \textcolor{black}{The two auxiliary functions in~\eqref{eqn:funcs} are the building blocks for many financial payoffs in options pricing.} For example, a call option has a payoff $\max(x-K,0)$ which can be written as
	\begin{equation*}
		\max(x-K,0) = x\1_{[K,\infty)}(x) - K\1_{[K,\infty)}(x),
	\end{equation*}
where the interval $I$ is $[K,\infty)$.

### 2018-01-04 UOW_thesis_template_v2-0/thesis_template/chapters/jumpImpVol.tex
:wrench: Removing the blue text after Marianito's approval

\subsection{Homogeneity of the solution}
First, we assume that the payoff function $\phi$ now depends on a parameter~$x' > 0$ (i.e., $\phi = \phi(x;x')$).  The motivation for this is that in the case of a European put or call, $x'$ represents the strike price. Furthermore, we assume that $\phi$ is homogeneous of degree one in~$x$ and $x'$. \textcolor{blue}{That is, we assume
$$
	\phi(\beta x; \beta x') = \beta \phi(x;x').
$$}
Note that standard put and call payoffs satisfy this assumption. We show that the option price function~$v$ is homogeneous of degree one in~$x$ and $x'$. That is, we want to show for $v = v(x,t; x')$ that
		\begin{equation}
			\label{eqn:homogen}
			v(\beta x, t; \beta x') = \beta v(x,t; x')
		\end{equation}
for all $\beta > 0$. This equality can be proven via a uniqueness argument as follows. We first express \eqref{eqn:PIDE} as $\mathscr{L} v = 0$. Now let $w = w(x,t; x')$ solve the following final value problem:
		\begin{align}
			\label{eqn:subPIDE}
			\begin{split}
			&\mathscr{L}w = 0, \qquad w(x,T; x') = \beta\phi(x;x').
			\end{split}
		\end{align}
Next, we define the function $v_1(x,t;x') = \beta v(x,t;x')$, where $v$ is a solution to (\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). Then
	\begin{align*}
		\mathscr{L}v_1 = \beta \mathscr{L}v = 0.
	\end{align*}
For the terminal condition, since $v(x,T;x') = \phi(x;x')$, this implies that
	\begin{equation*}
		v_1(x,T;x') = \beta v(x,T; x') = \beta\phi(x;x').
	\end{equation*}
Therefore $v_1$ satisfies the final value problem \eqref{eqn:subPIDE}. On the other hand, we now let $v_2(x,t,x') = v(\beta x, t; \beta x')$. Computing the derivatives gives
	\begin{equation*}
		\fr{\pr v_2}{\pr x} = \beta D_1v, \quad \fr{\pr^2 v_2}{\pr x^2} = \beta^2 D_{11}v,
	\end{equation*}
where $D_1$ and $D_{11}$ represent the first and second partial derivatives with respect to the first argument, respectively. Substituting these into (\ref{eqn:subPIDE}), we get
	\begin{align*}
		\mathscr{L}v_2 = \mathscr{L}v = 0,
	\end{align*}
and by the homogeneity of $\phi$, the terminal condition is
	\begin{align*}
		v_2(x,T;x') = v\left( \beta x, T; \beta x' \right) = \phi(\beta x; \beta x') = \beta \phi(x;x').
	\end{align*}
Hence $v_2$ also satisfies the final value problem \eqref{eqn:subPIDE}. By uniqueness, we have
	\begin{equation*}
		v\left(\beta x, t; \beta x'\right) = v_2(x,t;x') = v_1(x,t;x') = \beta v(x,t;x'),
	\end{equation*}
thus proving the homogeneity property for $v$ and any general payoff $\phi$ that is homogeneous of degree one in~$x$ and $x'$.

\subsection{Derivation of a Dupire-like PIDE via Euler's theorem on homogeneous functions}
The partial derivatives of the Dupire equation~\cite{Gatheral2006} are with respect to the strike price $K$. Thus to derive a Dupire-like PIDE, we will require partial derivatives in terms of $x'$ (the analogous variable for $K$). This can be done by invoking Euler's theorem for homogeneous functions~\cite[pp. 317]{Kishan2007} to $v$ and we get
	\begin{equation*}
		x\fr{\pr v}{\pr x} + x'\fr{\pr v}{\pr x'} = v,
	\end{equation*}
since $v$ has been shown to be homogeneous in $x$ and $x'$ of degree one. By differentiating the above equation with respect to $x$ and $x'$, we obtain
	\begin{equation*}
		x\fr{\pr^2 v}{\pr x^2} = -x'\fr{\pr^2 v}{\pr x \pr x'}, \quad x'\fr{\pr^2 v}{\pr x'^2} = -x\fr{\pr^2 v}{\pr x' \pr x},
	\end{equation*}
respectively. Hence it follows that
	\begin{equation*}
		x^2\fr{\pr^2 v}{\pr x^2} = x'^2\fr{\pr^2 v}{\pr x'^2}.
	\end{equation*}
The only term left to account for is the integral in (\ref{eqn:PIDE}). Notice that the first integrand term depends on~$y$; we want to transfer the dependency on $y$ to the third argument (i.e., $x'$). This can be achieved by the homogeneity property in (\ref{eqn:homogen}), and we obtain
	\begin{align*}
		v(xy,t; x') &= v\left(xy,t;\fr{x'y}{y}\right) = yv\left( x,t;\fr{x'}{y} \right).
	\end{align*}
Thus, setting $u(x',t; x) = v(x,t; x')$ and replacing all the $x$ derivatives with $x'$ derivatives and substituting the above rearrangement for the integrand, we get
	\begin{align}
		\label{eqn:DupireLike}
		\begin{split}
		\fr{\pr u}{\pr t} &- (q(t) + \kappa\lambda)u - (r(t) - q(t) - \kappa\lambda)x'\fr{\pr u}{\pr x'} + \fr{1}{2}\sigma(t)^2x'^2\fr{\pr^2 u}{\pr x'^2} \\
		& {} + \lambda \int_0^\infty \left( yu\left( \fr{x'}{y},t; x \right) - u(x',t; x) \right)f(y) \, \d y = 0
		\end{split}
	\end{align}
with
	\begin{equation}
		\label{eqn:DupireCond}
		u(x',T; x) = \phi(x';x),
	\end{equation}
since $u$ now depends on the variables $x'$ and $t$ with $x$ as a parameter. Equations~(\ref{eqn:DupireLike}) and (\ref{eqn:DupireCond}) together form the Dupire-like PIDE system for options in a jump-diffusion framework. Note that this reduces to the standard Dupire PDE as seen in \cite{Gatheral2006} in the absence of jumps (i.e., $\lambda = 0$) when $\phi$ is either the call or put payoff.

>>>>

\subsection{Homogeneity of the solution}
First, we assume that the payoff function $\phi$ now depends on a parameter~$x' > 0$ (i.e., $\phi = \phi(x;x')$).  The motivation for this is that in the case of a European put or call, $x'$ represents the strike price. Furthermore, we assume that $\phi$ is homogeneous of degree one in~$x$ and $x'$. \textcolor{black}{That is, we assume
$$
	\phi(\beta x; \beta x') = \beta \phi(x;x').
$$}
Note that standard put and call payoffs satisfy this assumption. We show that the option price function~$v$ is homogeneous of degree one in~$x$ and $x'$. That is, we want to show for $v = v(x,t; x')$ that
		\begin{equation}
			\label{eqn:homogen}
			v(\beta x, t; \beta x') = \beta v(x,t; x')
		\end{equation}
for all $\beta > 0$. This equality can be proven via a uniqueness argument as follows. We first express \eqref{eqn:PIDE} as $\mathscr{L} v = 0$. Now let $w = w(x,t; x')$ solve the following final value problem:
		\begin{align}
			\label{eqn:subPIDE}
			\begin{split}
			&\mathscr{L}w = 0, \qquad w(x,T; x') = \beta\phi(x;x').
			\end{split}
		\end{align}
Next, we define the function $v_1(x,t;x') = \beta v(x,t;x')$, where $v$ is a solution to (\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). Then
	\begin{align*}
		\mathscr{L}v_1 = \beta \mathscr{L}v = 0.
	\end{align*}
For the terminal condition, since $v(x,T;x') = \phi(x;x')$, this implies that
	\begin{equation*}
		v_1(x,T;x') = \beta v(x,T; x') = \beta\phi(x;x').
	\end{equation*}
Therefore $v_1$ satisfies the final value problem \eqref{eqn:subPIDE}. On the other hand, we now let $v_2(x,t,x') = v(\beta x, t; \beta x')$. Computing the derivatives gives
	\begin{equation*}
		\fr{\pr v_2}{\pr x} = \beta D_1v, \quad \fr{\pr^2 v_2}{\pr x^2} = \beta^2 D_{11}v,
	\end{equation*}
where $D_1$ and $D_{11}$ represent the first and second partial derivatives with respect to the first argument, respectively. Substituting these into (\ref{eqn:subPIDE}), we get
	\begin{align*}
		\mathscr{L}v_2 = \mathscr{L}v = 0,
	\end{align*}
and by the homogeneity of $\phi$, the terminal condition is
	\begin{align*}
		v_2(x,T;x') = v\left( \beta x, T; \beta x' \right) = \phi(\beta x; \beta x') = \beta \phi(x;x').
	\end{align*}
Hence $v_2$ also satisfies the final value problem \eqref{eqn:subPIDE}. By uniqueness, we have
	\begin{equation*}
		v\left(\beta x, t; \beta x'\right) = v_2(x,t;x') = v_1(x,t;x') = \beta v(x,t;x'),
	\end{equation*}
thus proving the homogeneity property for $v$ and any general payoff $\phi$ that is homogeneous of degree one in~$x$ and $x'$.

\subsection{Derivation of a Dupire-like PIDE via Euler's theorem on homogeneous functions}
The partial derivatives of the Dupire equation~\cite{Gatheral2006} \textcolor{black}{are with respect to the strike price $K$.} Thus to derive a Dupire-like PIDE, we will require partial derivatives in terms of $x'$ (the analogous variable for $K$). This can be done by invoking Euler's theorem for homogeneous functions~\cite[pp. 317]{Kishan2007} to $v$ and we get
	\begin{equation*}
		x\fr{\pr v}{\pr x} + x'\fr{\pr v}{\pr x'} = v,
	\end{equation*}
since $v$ has been shown to be homogeneous in $x$ and $x'$ of degree one. By differentiating the above equation with respect to $x$ and $x'$, we obtain
	\begin{equation*}
		x\fr{\pr^2 v}{\pr x^2} = -x'\fr{\pr^2 v}{\pr x \pr x'}, \quad x'\fr{\pr^2 v}{\pr x'^2} = -x\fr{\pr^2 v}{\pr x' \pr x},
	\end{equation*}
respectively. Hence it follows that
	\begin{equation*}
		x^2\fr{\pr^2 v}{\pr x^2} = x'^2\fr{\pr^2 v}{\pr x'^2}.
	\end{equation*}
The only term left to account for is the integral in (\ref{eqn:PIDE}). Notice that the first integrand term depends on~$y$; we want to transfer the dependency on $y$ to the third argument (i.e., $x'$). This can be achieved by the homogeneity property in (\ref{eqn:homogen}), and we obtain
	\begin{align*}
		v(xy,t; x') &= v\left(xy,t;\fr{x'y}{y}\right) = yv\left( x,t;\fr{x'}{y} \right).
	\end{align*}
Thus, setting $u(x',t; x) = v(x,t; x')$ and replacing all the $x$ derivatives with $x'$ derivatives and substituting the above rearrangement for the integrand, we get
	\begin{align}
		\label{eqn:DupireLike}
		\begin{split}
		\fr{\pr u}{\pr t} &- (q(t) + \kappa\lambda)u - (r(t) - q(t) - \kappa\lambda)x'\fr{\pr u}{\pr x'} + \fr{1}{2}\sigma(t)^2x'^2\fr{\pr^2 u}{\pr x'^2} \\
		& {} + \lambda \int_0^\infty \left( yu\left( \fr{x'}{y},t; x \right) - u(x',t; x) \right)f(y) \, \d y = 0
		\end{split}
	\end{align}
with
	\begin{equation}
		\label{eqn:DupireCond}
		u(x',T; x) = \phi(x';x),
	\end{equation}
since $u$ now depends on the variables $x'$ and $t$ with $x$ as a parameter. Equations~(\ref{eqn:DupireLike}) and (\ref{eqn:DupireCond}) together form the Dupire-like PIDE system for options in a jump-diffusion framework. Note that this reduces to the standard Dupire PDE as seen in \cite{Gatheral2006} in the absence of jumps (i.e., $\lambda = 0$) when $\phi$ is either the call or put payoff.
